### 2019-04-24 sections/language.tex
micro-optimise sentences in language section

Consider the following program.
\begin{TASK}
  enter Int >>= \n. if n == 42 then edit "Good" else edit "Bad"
\end{TASK}
Initially, the step is guarded because the editor does not have a value.
When users enter an integer, the program continues immediately with either \TS{edit "Good"} or \TS{edit "Bad"}, depending on the input.

@@

Consider this slight variation on \cref{exm:conditions}.
\begin{TASK}
  enter Int >>= \n. if n == 42 then edit "Good" else fail
\end{TASK}
The user is asked to enter an integer.
As long as the right hand side of $\Then$ evaluates to $\Fail$, the step cannot proceed, and the user can keep editing the integer.
As soon as the value of the left hand side is $42$, the right hand side evaluates to something other than $\Fail$, and the step proceeds to \TS{edit "Good"}.

@@

\lstset{emph={amount,start,now}}
With the language constructs seen so far it is possible to create a task that waits for a specified amount of time.
To do this,
we make use of a shared editor holding the current time (see \cref{sub:time}),
and a guarded internal step.
\begin{TASK}
  let wait : Int -> Task Unit = \amount : Int.
    update time >>= \start : Int.
    update time >>= \now : Int.
      if now >= start + amount then edit <<>> else fail
\end{TASK}
The first step is immediately taken, resulting in \TS{start} to be the time at the moment \TS{wait} is executed.
The second step is guarded until the current time is greater or equal to the start time plus the requested amount.

@@

A common pattern in workflow design is splitting up work into multiple tasks that can be executed simultaneously.
In \TOPHAT, all parallel branches can progress independently, driven by input events.
This requires input events to be tagged in order to reach the intended task.

@@

The task
\begin{TASK}
  enter Int <&> edit " Batman" >>= \<<n, s>>. edit (replicate n "Na" ++ s)
\end{TASK}
can only step when both editors have values.
When it steps, the continuation uses the pair of integer and string to calculate the result.

>>>>

Consider the following:
\begin{TASK}
  enter Int >>= \n. if n == 42 then edit "Good" else edit "Bad"
\end{TASK}
Initially, the step is guarded because the editor does not have a value.
When users enter an integer, the program continues immediately with either \TS{edit "Good"} or \TS{edit "Bad"}, depending on the input.

@@

Consider this slight variation on \cref{exm:conditions}:
\begin{TASK}
  enter Int >>= \n. if n == 42 then edit "Good" else fail
\end{TASK}
The user is asked to enter an integer.
As long as the right hand side of $\Then$ evaluates to $\Fail$, the step cannot proceed, and the user can keep editing the integer.
As soon as the value of the left hand side is $42$, the right hand side evaluates to something other than $\Fail$, and the step proceeds to \TS{edit "Good"}.

@@

\lstset{emph={amount,start,now}}
With the language constructs seen so far it is possible to create a task that waits for a specified amount of time.
To do this,
we make use of a shared editor holding the current time (see \cref{sub:time}),
and a guarded internal step.
\begin{TASK}
  let wait : Int -> Task Unit = \amount : Int.
    update time >>= \start : Int.
    update time >>= \now : Int.
      if now > start + amount then edit <<>> else fail
\end{TASK}
The first step is immediately taken, resulting in \TS{start} to be the time at the moment \TS{wait} is executed.
The second step is guarded until the current time is greater to the start time plus the requested \TS{amount}.

@@

A common pattern in workflow design is splitting up work into multiple tasks that can be executed simultaneously.
In \TOPHAT, all parallel branches can progress independently, driven by input events.
This requires inputs to be tagged in order to reach the intended~task. %%XXX: Hack to force `task` on the same line.

@@

The task
\begin{TASK}
  enter Int <&> edit " Batman" >>= \<<n, s>>. edit (replicate n "Na" ++ s)
\end{TASK}
can only step when both editors have values.
When it steps, the continuation uses the pair to calculate the result.
